---
title: "p8105_hw6_dna2118.Rmd"
author: "Dionna Attinson"
date: "11/21/2019"
output: html_document
---

```{r setup, include=FALSE}
library(viridis)
library(modelr)
library(mgcv)
library(patchwork)
library(tidyverse)
library(gridExtra)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(10)
```

### Problem 1
#### First, we will load in and clean the data. 
```{r}
birthweight_data = 
read.csv("./birthweight.csv") %>% 
  mutate(
    mrace = as.factor(mrace), 
    frace = as.factor(frace),
    babysex = as.factor(babysex), 
    malform = as.factor(malform)) %>% 
janitor::clean_names()
```
#### Now, we will propose a regression model. This regression model was chosen through previous research that has been done that demonstrates that mother's race and smoking status impact birthweight. 
```{r}
fit = lm(bwt ~  smoken + mrace + blength, data = birthweight_data)
summary(fit)
```
#### The following code chunk produces a plot of model residuals against fitted values using `add_predictions` and `add_residuals`. 
```{r}
birthweight_data %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid, color = resid)) +
  geom_point(alpha = 0.5) + 
  scale_color_viridis() +
  theme_minimal() +
  theme(legend.position = "none")
```


#### Now we will compare this regression models to two other models
* The first model will use length at birth and gestational age as predictors.
* The second model will use head circumference, length, sex, and all interactions (including the three-way interaction) between them. 
```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_data)
model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + babysex*blength + bhead*blength*babysex, data = birthweight_data)
```

#### We will then compare the three models in terms of the cross-validated prediction error, using `crossv_mc`.
```{r}
cv_df = 
  crossv_mc(birthweight_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = cv_df %>%
  mutate(fit = map(train, ~lm(bwt ~ smoken + blength + mrace, data = .x)),
         model1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + babysex*bhead + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_my_model = map2_dbl(fit, test, ~rmse(model = .x, data = .y)),
         rmse_comparison_1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_comparison_2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + 
  scale_fill_viridis_d(alpha = 0.5) + 
  theme_minimal() + 
  theme(legend.position = "none")
```

#### Through this violin plot, we get a sense of variance in prediction error and can compare prediction error distributions across methods. The comparison 2 model using head circumference, length, sex, and all interactions (including the three-way interaction) between them is the best model in this case.`

## Problem 2 
